---
title: "PA1_template"
author: "Bryan Kong Chak Bun"
date: "June 22, 2019"
output: html_document
---

###Introduction

With reference to the instruction of the Course Project 1, I have completed the my works in the same order as required.

###1. Code for reading in the dataset and/or processing the data
```{r Read_the_CSV_data}
# Read the CSV file
activity <- read.csv("activity.csv")
```

###2. Historgram of th total number of steps taken each day
```{r Histogram1}
# Call the "dplyr" package
library(dplyr)
# Group the data based on date and sum the steps in everyday
actHistData <- activity %>% group_by(date) %>% summarize(steps = sum(steps))
# Plot the histogram
with(actHistData, hist(steps, main="Total Number of Steps Taken in Each Day"))
```

###3. Mean and median number of steps taken each day
```{r Mean_and_Median}
# Return the mean value
mean(actHistData$steps,na.rm = TRUE)
# Return the median value
median(actHistData$steps, na.rm = TRUE)
```

###4. Time series plot of the average number of steps taken
```{r Time_series}
# Group the data by intervel and calculate the mean value with removing all "na"
actTimeSer <- activity %>% group_by(interval) %>% 
        summarise(steps = mean(steps, na.rm = TRUE))
# Plot the time serie
with(actTimeSer, plot(interval, steps, type = "l", 
                      main = "Average Number of Steps in 5 Min Intervals"))
```

###5. The 5-minute interval that, on average, contains the max number of steps
```{r Max_steps}
# Find the row with maximum steps
actTimeSer1 <- filter(actTimeSer, steps==max(steps))
# Return the interval value
actTimeSer1$interval
```

###6. Code to describe and show a strategy for imputing missing data
I firstly checked whether the value of step was "na". If yes, I found the interval of the missing value.  Then, I took the mean value (which was completed in above step) for placing the missing value.  The processing time would be quite long for this step,
```{r imputing_missing_value}
# Assign the orginal data with other name "act"
act <- activity
# Search every row
for (i in 1:nrow(act)) {
# Check whether the step variable was equal to na
        if (is.na(act[i, 1])==TRUE) {
                for (j in 1:nrow(actTimeSer)) {
                        if(actTimeSer[j,1] == act[i,3]){
# Search the same time interval from the result of above steps
                                act[i,1] <- actTimeSer[j,2]
                        }
                }
                
        }
}
```

###7. Historam of total no. of steps per date after missing value was imputed.
```{r New_histogram}
# Group the data by date and calculate the sum of the steps by date
actHist <- act %>% group_by(date) %>% summarize(steps = sum(steps))
# Plot the histogram
with(actHist, hist(steps, 
                   main="Total No of Steps Taken in Each Day(Imputting na"))
```

###8. Panel plot comparing the ave. no. of steps taking per interval across weekdays  and week ends
```{r Panel_plot}
# Change the value of date with the weekdays
actDate <- mutate(act, date = weekdays(as.Date(date)))
# Identify the weekday or weekend and change the variable of date
for (i in 1:nrow(actDate)) {
        if (actDate[i,2] == "Saturday" | actDate[i,2] == "Sunday") {
                actDate[i,2] <- "weekend" }
                else {
                        actDate[i,2] = "weekday"
                }
}
# Grop the data by interval and by date, calculate the mean value of the steps
actDateData <- actDate %>% group_by(interval, date) %>% summarise(steps = mean(steps))
# Set the graph in two rows and one column
par(mfrow=c(2,1))
# Plot the first graph showing avarge steps time series in weekdays
plot(subset(actDateData, date =="weekday")$interval, 
     subset(actDateData, date =="weekday")$steps, type = "l",
     xlab="Interval", ylab = "Average Steps", main = "Weekday")
# Plot the second graph showing average steps time series in weekend   
plot(subset(actDateData, date =="weekend")$interval, 
     subset(actDateData, date =="weekend")$steps, type = "l",
     xlab="Interval", ylab = "Average Steps", main = "Weekend")
```

All of above R code can reproduced the reproduce the results in this report.